Tutorials: A Brief Overview

### 2023-04-24 howto.qmd
divio docs section's update

[Section in progress...]

>>>>

The "how-to" section focuses on providing practical solutions to specific methods or problems users might encounter. Unlike tutorials, which aim to teach a concept, how-to guides concentrate on the efficient execution of specicif analyses without going into in-depth background explanations. By following these principles, the how-to section aims to create practical, efficient, and user-friendly guides that help users quickly identify solutions and accomplish their goals.

The how-to section should:

1. Be problem-oriented: How-to guides should address specific problems or analyses users may face, offering clear and concise solutions. Each guide should focus on a single issue, making it easy for users to find and apply the relevant information.

2. Offer step-by-step instructions: Similar to tutorials, how-to guides should provide a clear sequence of steps that users can follow to solve their problem or complete their analysis. Each step of the instructions should be explained in a straightforward manner.

3. Be concise: How-to guides should be to the point, offering just enough information to help users accomplish their goal. This means avoiding unnecessary explanations or background information, as users are typically looking for a quick solution.

4. Be actionable: The content in the how-to section should be practical, with a focus on actionable advice that users can apply immediately. This may involve providing code snippets, configuration settings, or other specific instructions that users can implement in their projects.

5. Include examples: How-to guides should include relevant examples that demonstrate the solution in action, allowing users to see how the instructions can be applied in a real-world context.

6. Cross-reference other resources: How-to guides should link to other relevant documentation, such as explanations or reference material, for users who may require additional background information or a deeper understanding of the topic.

For additional information/resources, see [https://documentation.divio.com/]

### 2023-04-24 reference.qmd
divio docs section's update

[Section in progress...]

>>>>

The "Reference" section focuses on providing accurate, concise, and structured information about specific components, functions, or features of a method, analysis, or framework. Unlike tutorials, how-to guides, and explanations, which aim to teach, solve problems, and provide context, respectively, reference materials serve as a quick lookup resource for users to find the exact information they need. By following these principles, the reference section aims to create a reliable, user-friendly, and easily searchable resource that provides users with the specific information they need to effectively use and understand the method, analysis, or framework.

The reference section should:

1. Be comprehensive: Reference materials should cover all relevant aspects of the method, analysis, or framework, including components, functions, features, and configurations. The goal is to provide users with a complete and authoritative source of information.

2. Be accurate: The information in the reference section should be precise and up-to-date, ensuring that users can rely on it for their projects. This may involve regular updates and checks to maintain accuracy.

3. Be concise: Reference materials should be brief and to the point, providing just enough information for users to understand and use the specific analysis or method. This means avoiding unnecessary explanations, examples, or background information.

4. Follow a consistent format: The reference section should use a consistent format and structure, making it easy for users to locate and access the information they need. This may involve using templates, standardized headings, or other organizational tools.

5. Be easily searchable: Reference materials should be designed with searchability in mind, enabling users to quickly find the information they need. This may involve using clear and descriptive titles, headings, and keywords, as well as implementing search functionality or indexing.

6. Cross-reference other resources: The reference section should link to other relevant documentation, such as tutorials, how-to guides, or explanations, for users who may require additional information or a deeper understanding of the topic.

For additional information/resources, see [https://documentation.divio.com/]

### 2023-04-24 tutorials.qmd
cli commit 3
divio docs section's update

[Section in progress...]

>>>>

The primary goal of the tutorial section is to help users learn and understand a specific topic or method by providing an introductory and hands-on, step-by-step guide. This section aims to create engaging, accessible, and effective entry learning experiences that enable users to develop their skills and understanding of the subject matter.

The tutorial section should:

1. Be goal-oriented: Tutorials should focus on a specific task the user wants to accomplish. By concentrating on a particular outcome, the tutorial becomes more engaging and relevant to the user.

2. Provide clear steps: Tutorials should offer step-by-step instructions, guiding users through the process of achieving their goal. Each step should be clearly explained and easy to follow, making sure users can successfully complete the tutorial.

3. Use examples: Tutorials should include real-world examples and use cases that are relatable and meaningful to the user. This helps users better understand the concepts being taught and how they can apply them in their own projects.

4. Be practical: Tutorials should emphasize hands-on learning, encouraging users to actively engage with the content and practice the skills they are learning. This may involve providing code samples, interactive exercises, or other activities that help users develop their understanding.

5. Encourage exploration: Tutorials should encourage users to explore and experiment with the concepts they are learning. This may involve providing opportunities for users to adapt the tutorial to their own needs or offering suggestions for further experimentation.

For additional information/resources, see [https://documentation.divio.com/]
